No need to know: astrophysics-free gravitational-wave cosmology

### 2024-04-02 src/tex/ms.tex
[showyourwork] overleaf sync

The code used to generate all simulated data, perform the population inference, and create all figures in this paper is made publicly available at \url{https://github.com/afarah18/spectral-sirens-with-GPs}. %\GitHubURL{}, and was enabled by the \showyourwork package \citep{Luger2021}.

>>>>

The code used to generate all simulated data, perform the population inference, and create all figures in this paper is made publicly available at \GitHubURL{}, and was enabled by the \showyourwork package \citep{Luger2021}. %\url{https://github.com/afarah18/spectral-sirens-with-GPs}. %
